### 2021-05-24 README.Rmd
updated README with correct DOI and journal information, removed possible journal sections

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Estimating total escapment past Lower Granite Dam using all possible data"
```

@@

> See, K.E., R.N. Kinzer and M.W. Ackerman, (2020). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> See, K.E., R.N. Kinzer and M.W. Ackerman, (2020). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> See, K.E., R.N. Kinzer and M.W. Ackerman, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "State-Space Model to Estimate Salmon Escapement Using Multiple Data Sources"
```

@@

> See, K.E., R.N. Kinzer and M.W. Ackerman (2021). _`r Title`_. North American Journal of Fisheries Management <https://doi.org/10.1002/nafm.10649>

@@

> See, K.E., R.N. Kinzer and M.W. Ackerman (2021). _`r Title`_. North American Journal of Fisheries Management, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.1002/nafm.10649>

@@

> See, K.E., R.N. Kinzer and M.W. Ackerman (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.1002/nafm.10649>
